Ejemplificando art

### 2023-07-27 notebooks/example_script.Rmd
Makes the figure outputs "square" so the directions of the vectors can be better understood

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output: word_document
editor_options:
  markdown:
    canonical: true
---

>>>>

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output:
  word_document:
    fig_width:  6
    fig_height: 6
editor_options:
  markdown:
    canonical: true
---
